On the Galaxy Size--Halo Connection

### 2017-08-30 paper/galsize_paper.tex
Finished baseline simulation and model discussion

\subsection{Galaxy Sample}
\label{subsec:galaxydata}

@@

We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}. In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively. We cross-match our DR10 sample against the \citet{meert_etal15} scale radii and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalfbulge,\rhalfdisk,$ and $\bt.$ Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.

\subsection{Clustering Measurements}
\label{subsec:clusteringmeasurements}

@@

@@

\subsubsection{Mapping $\mstar$ and $\sfr$ to halos}
\label{subsubsec:umachine}

@@

\subsubsection{Mapping $\bt$ decomposition to halos}
\label{subsubsec:random_bt_model}

>>>>

\subsection{Galaxy Sample and Measurements}
\label{subsec:galaxydata}

@@

We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}. In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively. We cross-match our DR10 sample against the \citet{meert_etal15} scale radii and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalfbulge,\rhalfdisk,$ and $\bt.$

@@

Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.

\subsection{Simulation and Halos}
\label{subsec:sim}

{\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation are the basis of all our modeling.

@@

\subsubsection{Mapping $\mstar$ \& $\sfr$ to halos}
\label{subsubsec:umachine}

@@

\subsubsection{Mapping $\bt$ to halos}
\label{subsubsec:random_bt_model}
